\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
working on revisions

We would like to thank Atticus Sims, CEO and founder of Kyoto VR, for sponsoring
this project and providing help and guidance throughout our time in Japan. His
knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
to our experience.

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.

@@

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was dictated by Atticus Sims, C.E.O and founder of Kyoto VR, who plans to
monetize the app. We also worked with an IQP team, who had been tasked with
exploring funding options and creating promotional content.

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

@@

Before our project started, Kyoto VR was already using an app to deliver audio
tours. The app, called izi.TRAVEL, allows users to create audio tours with
audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too.  Kyoto VR used the platform to make a simple audio tour
of Kinkaku-ji.

@@

As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
rapidly testing your ViroReact app on native hardware without the need for an
emulator. In the root directory of your project, you can launch a Node server
with the command \texttt{npm start}. From here, you can input the provided URL
into the Viro Media app. This will quickly download the code, graphics, and 3D
object files from the server and launch a functional version of the app
\autocite{viro-testbed2019}. This allowed us to get a real AR app up and
running on our devices much more easily than any of the other
frameworks/engines we explored. Unfortunately, the test bed app was somewhat
unreliable based on our experience; the test bed would frequently crash or
would not be able to download the files from the Node server. The most reliable
way to test our app was to compile a binary and manually install it onto our
devices, which completely defeats the purpose of the test bed app.

@@

@@

Kinkaku-ji, the Temple of the Golden Pavilion, is undoubtedly one of Japan's
greatest attractions.  As of September 2019, it was the second-most visited site
in Kyoto---second only to Kyoto Station \autocite{japanguide2019}. Kinkaku-ji's
rich history and stunning beauty bring tourists from all over the world to see
its shining gold walls and magnificent gardens. Our project intends to enhance
user's enjoyment and understanding of Kinkaku-ji through informative interactive
media, teaching about the history and significance of the site.

@@

In 1950 the pavilion was burned down by a paranoid schizophrenic monk who had
been living at the temple~\autocite{borowitz2005}. The structure was rebuilt in
1955, close to the original design but with more extensive gold
leaf~\autocite{bornoff2000}. The interior was also restored later.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map, edit those regions and assign media to each of
the drawn regions.

An audio file and multiple image files can be uploaded for each region the user
defines. The user can also provide a text transcript of the audio file as well.
After naming and uploading the tour with the ``Upload'' button, our backend
builds a zip containing a folder that can be placed directly into the Unity
project.

Our backend allows users to save their tours to our server and load those same
tours back into the editor to resume work.  The geographic area of each region
can be adjusted by clicking and dragging. Vertices can also be added and
deleted if the needs of the tour change over time.

\subsubsection{The Need for an Editor}
\label{sec:theNeedForAnEditor}

One of the goals for our project is to create a working prototype that others
can build off of in the future.

Similar to the app izi.TRAVEL discussed in Section~\ref{sec:iziTravel}, we
needed some way to easily define arbitrary polygons (which we call ``regions'')
and associate media with each one, such as audio and image files.

For testing purposes, we initially defined these regions directly in the C\#
Scripts, hard-coding the coordinates. Below is an example of a quadrilateral
surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu campus.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
not convenient. Atticus reminded us that, although he has a working knowledge of
Unity, he is not a software developer. In order to make our app prototype at all
useful for the future, we needed to provide an easy way to ``design'' a tour.

@@

Here is an example of the JSON metadata generated by Editour:

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 34.979222, "lng": 135.963628}, ... ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ],
         "transcript": "To your left, you can see a beautiful place."
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 34.979754, "lng": 135.964889}, ... ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
         "transcript", "To your right, you can see a gorgeous place."
      }
   ]
}
\end{minted}

Within each object in the region list, we can see that the region has five
properties: a name, a list of coordinates, a list of audio files, a list of
multiple image files, and a transcript of the audio file. (In the current
design of the app, it only makes sense to associate one audio file per region,
but the format makes it easy to accommodate for multiple audio files in the
future.) One disadvantage is that all media files have to have unique names.
This is because the zip that is created by the Editour backend contains all of
the media files in a flat file structure. The above JSON is used to associate
each media file with a region, meaning that the filename needs to act as a
primary key. The backend will respond with a message if this is the case,
prompting the user to have unique names for all files.

@@

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started.  A user can only
terminate the polygon after two points have been placed to prevent the user
from drawing a region with an area of zero. Once a region is created, a region
card appears in the side bar. From here, the user can edit anything about the
region. From here, the user can edit anything about the region.

@@

The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
subcard, which is fairly self-explanatory.  This section expands to reveal a
textbox, allowing the user to rename the region after clicking ``Okay'' or
hitting the enter key. (There are multiple places in the UI where a textbox is
immediately adjacent to a ``Confirm'' button.  We made sure all of these can be
triggered by simply hitting enter, since this is common when filling out
forms.)

@@

The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly involved.
Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
of options for augmenting the audio, images and text to be associated with that
region of the tour. From here, the user can upload an audio file and multiple
image files from his or her hard drive with the two file-select fields. If the
tour has been downloaded as a server, the names of the files already present on
the server will appear as cards with `X' buttons. This allows the user to
remove images or audio from that region even after the tour has been uploaded.

@@

The third subcard is the ``Edit'' subcard. This subcard can be revealed in one
of two ways. The first way is by clicking on the yellow bar labeled ``Edit'',
which is the same for all subcards. Alternatively, the user can also click
directly on the region on the map. The region will flash yellow and be scrolled
into view to let the user know which region was clicked on. Both of these
methods will enable editing mode, whereby the user can directly manipulate the
vertices that make up the region. Blue circles appear on top of each vertex,
and red circles appear at the midpoint of each edge. Clicking on a red midpoint
will add an additional vertex at that midpoint. Dragging one of the blue
vertices will do as you might expect---move the vertex around. The latitude and
longitude are updated in the ``Edit'' subcard as the user drags the vertex
around. Clicking on the vertex directly will create a blue pin-shaped marker
that the user can also drag around. Clicking on the coordinate box in the
subcard will also create this blue pin-shaped marker; the map will also pan to
this coordinate. The user can also delete vertices in the same way that files
can be deleted from the ``Media'' subcard by clicking on the `X' button. If there
are exactly three points in a region, the `X' buttons will be ``grayed-out'',
preventing the user from deleting any more points (since a polygon must consist
of at least three points.)

\begin{figure}[h]
	\centering
    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Edit'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete''.
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
region he or she did not mean to.

@@

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
a ``Success'' message will appear. If there was some problem, the error message
returned by the server is displayed in this box instead. Since uploading,
downloading and deleting are all network-related operations, it makes sense to
include this message box for each card.

@@

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. The download
card containing a box filled with filenames on the server can be seen in
Figure~\ref{fig:downloadCard}.

@@

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

@@

Once a tour is either uploaded or downloaded, a link to download the zip file
will appear. The zip file contains all of the uploaded media, and a metadata
file. The metadata is in the form of a JSON file; it contains all of the
latitudes, longitudes, and enough information to associate all of the media
with the correct regions. This is the file that we unzip and place into the
Unity project before it is compiled. This also is useful if the user wants to
check the audio and image files that were uploaded.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

The server-side backend of the Editour application is written in JavaScript for
Node.js. This backend both serves the static frontend content and runs
server-side scripts that process incoming API requests.  We chose Node.js as the
server-side framework because of our prior experience with JavaScript, its
high-performing asynchronous architecture~\autocite{orsini2013}, and its ease of
development.

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts, which zips up the files and
saves them to the server's disk with a timestamp. Then any application can
request a particular tour and the backend will serve the most recent version of
it.

As previously mentioned in \ref{sec:editingATour}, our web application allows
users to edit existing tours. When the user requests to edit a tour on the
frontend it sends a request to the backend server for that tour's metadata
file. This file contains information about all regions and files in the tour.
The user can then edit the regions, change names, upload new files, or delete
existing ones without ever having to download the other tour files from the
server, which could take a long time depending on their size. When the user is
done editing they can upload the new metadata and any newly added files to the
server, which intelligently collects new and old files required by the tour and
zips them into a new tour file on the disk.

@@

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and
shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
environment was designed for running simple PHP applications like WordPress, so
it took a bit of work to coerce it into running a Node.js application.

We were able to get shell access to the shared hosting environment, but without
superuser privileges. This meant we couldn't install packages, change system
settings, or access \texttt{systemctl}. In order to install Node.js and npm in
this environment we had to use Node Version Manager, a series of shell scripts
that handles downloading and compiling various versions of
Node~\autocite{nvmsh2019}.  The only difficulty with this was finding a version
of Node.js that could compile with the older version of GCC the RHEL server had.
Fortunately the server already had git installed, so we were able to simply
clone the backend from GitHub and run it with npm.

However, the server already had Apache listening on port 80, and without
superuser privileges we could not edit the Apache configuration files to change
this. Instead we decided to configure Apache as a reverse proxy, using only the
rules that can be put in a \texttt{.htaccess} file, since this is the only
configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
we were able to rewrite incoming requests on port 80 to instead go to
\texttt{localhost:3000}, the port where Node.js was
listening~\autocite{apache2019}.

@@

Tours are stored on the server as compressed \texttt{.zip} files, but when
uploading or editing a tour these zips are decompressed to a temporary
directory. To prevent the server's limited disk space from filling up with old
temporary files we wrote a simple bash script that removes directories that
haven't been modified in the past five days. We set up a \texttt{cron} job to
run this script automatically once per day to clean out old temporary files that
aren't being used any more.

Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto VR can get
a better hosting provider we consider it a minor issue.

@@

In the current implementation, the tour file generated by the Editour backend
still has to be moved manually to the Unity project folder. In the future, we
would like the app to be able to contact a server running a version of the
Editour backend and update the tour info by itself. This would allow Kyoto VR
to update the tours without updating the entire app.

@@

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely Japanese.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. Then, the user is prompted to
highlight where text appears in the photo. After the translation is complete,
the translated text appears in a separate UI element instead superimposed onto
the photo. In most cases, it is more convenient and readable to have the
translation appear in a separate scrollable textbox. This motivated the current
design of the ``info buttons'' in ARuko. Instead of placing text directly onto
signage, we place a blue button with an `i' in the center. By tapping on this
button, a separate UI element will appear containing the translated text. Since
this button is cast into the world using the AR camera, the button is
intuitively placed directly onto the content in the real world.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.3\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

The early UI was very much a product of ARuko's development; many of it's
elements were created as new features were added. But as more features were
added, it became clear that the UI couldn't consist simply of buttons and 
other basic features provided by Unity. We would need to learn more about 
how to create more interesting and useful UI elements to accomodate for 
our new functionality.

@@

While testing we discovered some issues with the design of the tour. One
region was completely misplaced, so the audio played at the wrong time while
walking through the area. Several other regions were too big, so the audio
started playing long before the user was actually near the feature it was
discussing. Using the Editour web-app, we were able to correct quickly these
issues with the tour design once we returned to Atticus' office.

@@

Atticus Sims proposed the idea of working with Michael Whittle. Michael Whittle
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo exhibitions and group exhibitions across the world,
including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
Kyoto VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.

>>>>

We would like to thank Atticus Sims, CEO and founder of Kyoto~VR, for sponsoring
this project and providing help and guidance throughout our time in Japan. His
knowledge of the history of Kinkaku-ji and Kyoto in general has been invaluable
to our experience.

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.

@@

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections \ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was dictated by Atticus Sims, C.E.O and founder of Kyoto~VR, who plans to
monetize the app. We also worked with an IQP team, who had been tasked with
exploring funding options and creating promotional content.

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto~VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

@@

Before our project started, Kyoto~VR was already using an app to deliver audio
tours. The app, called izi.TRAVEL, allows users to create audio tours with
audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too.  Kyoto~VR used the platform to make a simple audio tour
of Kinkaku-ji.

@@

As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
rapidly testing your ViroReact app on native hardware without the need for an
emulator. This allowed us to get a real AR app up and running on our devices
much more easily than any of the other frameworks/engines we explored.
Unfortunately, the test bed app was somewhat unreliable based on our
experience; the test bed would frequently crash or would not be able to
download the files from the server. The most reliable way to test our app was
to compile a binary and manually install it onto our devices, which completely
defeated the purpose of the test bed app.

@@

%TODO write this section
TODO: write this section

@@

Kinkaku-ji, the Temple of the Golden Pavilion, is undoubtedly one of Japan's
greatest attractions.  As of September 2019, it was the second-most visited site
in Kyoto---second only to Kyoto Station \autocite{japanguide2019}. Kinkaku-ji's
rich history and stunning beauty bring tourists from all over the world to see
its shining gold walls and magnificent gardens. Our project intends to enhance
users' enjoyment and understanding of Kinkaku-ji through informative interactive
media, teaching about the history and significance of the site.

@@

In 1950 the pavilion was burned down by a paranoid schizophrenic monk who had
been living at the temple~\autocite{borowitz2005}. The structure was rebuilt in
1955, close to the original design but with more extensive gold
leaf~\autocite{bornoff2000}. The interior was also restored later to match the
original.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web app. At its core, Editour is a tool to draw arbitrarily-shaped
geographic regions onto a map, edit those regions and assign media to each of
the drawn regions.

An audio file and multiple image files can be uploaded for each region the user
defines. The user can also provide a text transcript of the audio file as well.
After naming and uploading the tour with the ``Upload'' button, our backend
builds a zip containing files that can be placed directly into the Unity
project.

Our backend allows users to save their tours to a server and load those same
tours back into the editor to resume work. The geographic area of each region
can be adjusted by clicking and dragging. Vertices can also be added and
deleted if the needs of the tour change over time.

\subsubsection{The Need for an Editour}
\label{sec:theNeedForAnEditour}

One of the goals for our project is to create a working prototype that others
can build off of in the future. Similar to the app izi.TRAVEL discussed in
Section~\ref{sec:iziTravel}, we needed some way to easily define arbitrary
polygons (which we call ``regions'') and associate media with each one, such as
audio and image files.

For testing purposes, we initially defined these regions directly in the C\#
scripts, hard-coding the coordinates. Below is an example of a quadrilateral
surrounding the Creation Core building at the Ritsumeikan Biwako-Kusatsu campus.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
cumbersome. Atticus is not a software developer, and does not want to work with
C\# scripts. In order to make our app prototype at all useful for the future,
we needed to provide an easy way to ``design'' a tour using a simple graphical
interface.

@@

Here is an example of a tour metadata file in JavaScript Object Notation (JSON)
format:

\begin{minted}{json}
{
   "regions": [
      {
         "name": "Beautiful Place",
         "points": [ {"lat": 34.979222, "lng": 135.963628}, ... ],
         "audio": [ "beautiful-audio.mp3" ],
         "images": [ "mountain.jpg", "stream.jpg" ],
         "transcript": "To your left, you can see a beautiful place."
      },
      {
         "name": "Gorgeous Place",
         "points": [ {"lat": 34.979754, "lng": 135.964889}, ... ],
         "audio": [ "gorgeous-audio.mp3" ],
         "images": [ "hill.jpg", "valley.jpg", "gorge.jpg" ],
         "transcript": "To your right, you can see a gorgeous place."
      }
   ]
}
\end{minted}

Within each object in the region list, we can see that the region has five
properties: a name, a list of coordinates, a list of audio files,\footnote{In
the current design of the app, it only makes sense to associate one audio file
per region, but the format makes it easy to accommodate for multiple audio
files in the future.} a list of multiple image files, and a transcript of the
audio file. One disadvantage is that all media files have to have unique names.
This is because the zip that is created by the Editour backend contains all of
the media files in a flat file structure. The above JSON is used to associate
each media file with a region, meaning that the filename needs to act as a
unique identifier. The backend will respond with a message if it finds
duplicate filenames, prompting the user to use unique names for all files.

@@

The user can easily create a new region by shift-clicking the map, and then
continuing to click to define more points. Figure~\ref{fig:drawingRegion} shows
this in action. To terminate the polygon, the user must shift-click again. The
``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started. A user can only
terminate the polygon after two points have been placed to prevent the user
from drawing a region with an area of zero. Once a region is created, a region
card appears in the side bar. From here, the user can edit anything about the
region.

@@

The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
subcard, which is fairly self-explanatory.  This section expands to reveal a
textbox, allowing the user to rename the region after clicking ``Okay'' or
hitting the enter key.\footnote{There are multiple places in the UI where a
textbox is immediately adjacent to a ``Confirm'' button.  We made sure all of
these can be triggered by simply hitting enter, since this is common behavior
when filling out forms on the web.}

@@

The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly more
involved. Expanding the ``Media'' subcard by clicking on the green bar will
reveal a bevy of options for augmenting the audio, images, and text to be
associated with that region of the tour. From here, the user can upload an
audio file and multiple image files from his or her hard drive with the two
file-select fields. If the user is editing an existing tour that has already
been uploaded, the names of the files already present on the server will appear
as cards with `X' buttons. This allows the user to remove images or audio from
that region even after the tour has been uploaded.

@@

The third subcard is the ``Points'' subcard. This subcard can be revealed in
one of two ways. The first way is by clicking on the yellow bar labeled
``Points'', which is the same for all subcards. Alternatively, the user can
click directly on the region on the map. The region will flash yellow and be
scrolled into view to let the user know which region was clicked on. Both of
these methods will enable editing mode, whereby the user can directly
manipulate the vertices that make up the region. Blue circles appear on top of
each vertex, and red circles appear at the midpoint of each edge. Clicking on a
red midpoint will add an additional vertex at that midpoint. Dragging one of
the blue vertices will move the vertex around. The latitude and longitude are
updated in the ``Points'' subcard as the user drags the vertex around. Clicking
on the vertex directly will create a blue pin-shaped marker that the user can
also drag. Clicking on the coordinate box in the subcard will also create this
blue pin-shaped marker; the map will also pan to this coordinate. The user can
also delete vertices in the same way that files can be deleted from the
``Media'' subcard by clicking on the `X' button on that vertex's coordinate
card. If there are exactly three points in a region, the `X' buttons will be
``grayed-out,'' preventing the user from deleting any more points, since a
polygon must consist of at least three points.

\begin{figure}[h]
	\centering
    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Points'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete.''
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!'' This prevents the user from accidentally deleting a
region he or she did not mean to remove.

@@

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{fig:uploadingMessage}. If an HTTP 200 (OK) or 201 (Created)
code~\autocite{rfc7231} is returned from the server, a ``Success'' message will
appear. If there was some problem, the error message returned by the server is
displayed in this box instead. Since uploading, downloading, and deleting are
all network-related operations, it makes sense to include this message box for
each card.

@@

When the page is loaded, the frontend will request the names of the tour files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. This feature
can be seen in figure Figure~\ref{fig:downloadCard}. Clicking ``Download'' does
not download the tour to the user's computer. Instead, it requests only the
tour metadata from the server so the tour's data can be displayed in the web
app. The user can then edit the tour and upload a new version.

@@

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button to pan to the specified location. We also hard-coded a few
shortcuts for places that Atticus might want to design a tour for in the future,
which can be accessed by clicking on the yellow buttons with place names.

@@

Once a tour is either uploaded or downloaded, a link to download the zip file of
that tour will appear. The zip file contains all of the uploaded media, and a
metadata file. The metadata is in the form of a JSON file; it contains all of
the latitudes, longitudes, and enough information to associate all of the media
with the correct regions. The downloaded zip file is what we decompress and
place into the Unity project before it is compiled. This feature is also useful
if the user wants to check the audio and image files that were uploaded.

%update this figure
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

The server-side backend of the Editour application is written in JavaScript for
Node.js. This backend both serves the static frontend content and runs
server-side scripts that process incoming application programming interface
(API) requests. We chose Node.js as the server-side framework because of our
prior experience with JavaScript, its high-performing asynchronous
architecture~\autocite{orsini2013}, and its ease of development.

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts. The server zips up the files
and saves them to the disk with a timestamp. Then any application can request a
particular tour and the backend will serve the most recent version.

As previously mentioned in Section~\ref{sec:editingATour}, our web application
allows users to edit existing tours. When the user requests to edit a tour on
the frontend it sends a request to the backend server for that tour's metadata
file. This file contains information about all regions and files in the tour.
The user can then edit the regions, change names, upload new files, or delete
existing ones without ever having to download the other tour files from the
server, which could take a long time depending on their size. When the user is
done editing they can upload the new metadata and any newly added files to the
server, which intelligently collects new and old files required by the tour and
zips them into a new tour file on the disk.

@@

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and a
shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
environment was designed for running simple PHP applications like WordPress, so
it took a bit of work to coerce it into running a Node.js application.

We were able to get shell access to the shared hosting environment, but without
superuser privileges. This meant we could not install packages, change system
settings, or access \texttt{systemctl}, the command that manages systemd
services. In order to install Node.js and npm in this environment we had to use
Node Version Manager, a series of shell scripts that handles downloading and
compiling various versions of Node~\autocite{nvmsh2019}.  The only difficulty
with this was finding a version of Node.js that could compile with the older
version of GCC that the RHEL server had. After resolving this challenge, we were
able to simply clone the backend from GitHub and run it with npm.

However, the server already had Apache listening on port 80, and without
superuser privileges we could not edit the Apache configuration files to change
this. Instead we decided to configure Apache as a reverse proxy, using only the
rules that can be put in a \texttt{.htaccess} file,\footnote{This is a
directory-level configuration file with limited options compared to Apache's
global configuration files.} since this is the only configuration file we could
access. Using Apache's \texttt{mod\_rewrite} module we were able to rewrite
incoming requests on port 80 to instead go to \texttt{localhost:3000}, the port
where Node.js was listening~\autocite{apache2019}.

@@

Tours are stored on the server as compressed zip files, but when uploading or
editing a tour these zips are decompressed to a temporary directory. To prevent
the server's limited disk space from filling up with old temporary files we
wrote a simple bash script that removes directories that have not been modified
in the past five days. We set up a cron job\footnote{The program cron allows for
periodic scheduling of repeated commands} to run this script automatically once
per day to clean out old temporary files that are not being used any more.

Unfortunately, the hosting solution Kyoto~VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto~VR can get
a better hosting provider we consider it a minor issue.

@@

In the current implementation, the tour file generated by the Editour backend
still has to be moved manually to the Unity project folder. In the future, we
would like the app to be able to contact a server running a version of the
Editour backend and update the tour info by itself. This would allow Kyoto~VR
to update the tours without updating the entire app.

@@

Despite Kinkaku-ji being an incredibly popular tourist destination that draws
crowds from all over the world, the majority of the signage is purely Japanese.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable textbox. This motivated the current design of the ``info buttons'' in
ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

The early UI was very much a product of ARuko's development; many of it's
elements were created as new features were added. But as more features were
added, it became clear that the UI could not consist simply of buttons and 
other basic features provided by Unity. We would need to learn more about 
how to create more interesting and useful UI elements to accomodate for 
our new functionality.

@@

While testing we discovered some issues with the design of the tour. One
region was completely misplaced, so the audio played at the wrong time while
walking through the area. Several other regions were too big, so the audio
started playing long before the user was actually near the feature it was
discussing. Using the Editour web app, we were able to correct quickly these
issues with the tour design once we returned to Atticus' office.

@@

Atticus Sims proposed the idea of working with Michael Whittle. Michael Whittle
received his PhD at the Kyoto City University of Arts in 2014. His art has
appeared in dozens of solo exhibitions and group exhibitions across the world,
including Kyoto, Beijing, London and New York~\autocite{michaelwhittle2019}.
Kyoto~VR has worked with Michael Whittle in the past to create a 3D scan of a
solo exhibition, `Portraits of Thought'. This exhibition displayed diagrams
inspired by real science and mathematics. Atticus provided us with some
diagrams to test in the Vuforia developer portal, since Michael Whittle wanted
to know how well certain pieces of art would work as AR image targets. All of
images that were provided to us were ranked as ``five stars'' by Vuforia,
indicating that those images would serve well as AR image targets.
